Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
catalogs

The majority of the stars in the high-$K$ sample have poorly constrained orbital
parameters because the posterior pdfs are very multimodal.

@@

\todo{Many examples of stars that meet K cut but solutions limited to a few
qualitatively different solutions}

@@

\todo{Stars with Martig or Ness masses - m2min}

@@

\todo{Period-eccentricity plot - tidal circularization}

>>>>

The majority of the stars in the high-$K$ sample have poorly constrained orbital
parameters because the posterior pdfs are very multimodal.
The high-$K$ sample includes all stars in the catalogs described in the next two
subsections, however these two catalogs are mutually exclusive with one another.

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
just a few qualitatively different solutions.
For these stars, one or a few more well-timed RV measurements would likely lead
to uniquely-determined orbital parameters.
\todo{How exactly do we select these stars?}

\figurename~\ref{fig:todo} shows a few examples of stars that meet these
criteria.
Note that in these cases, there are certain times at which a future observation
would be far more informative: For example, \todo{top panel, time X vs. time Y}.

\todo{Describe catalog contents: Also include M2_min and primary mass when
possible?}

@@

\todo{Should figures be phase-folded?}

\todo{Also include M2_min and primary mass when possible?}

@@
